### 2020-07-25 draft.Rmd
Switch assignment operators to equals signs

```{r load-data}
seed011204 <-read_stata("dataverse_files/seedanalysis_011204_1.dta")

seed080404 <- read_stata("dataverse_files/seedanalysis_080404_1.dta")

combined <- read_stata("dataverse_files/seedanalysis_011204_080404_1.dta")

six_months <- filter(seed011204, !is.na(treatment))

@@

combined <- combined  %>%
  # turn dollars into hundreds of dollars
  mutate(
    totbal = totbal / 100,
    newtotbal = newtotbal / 100
  ) %>%
  # fix population variable
  mutate(pop = as.numeric(str_replace(pop, ",", ""))) %>%
  # create bank penetration variable%>%
  mutate(brgy_penetration = no_clients / pop)

combined <- combined %>%
  # calculate the mean and sd for each bank
  # the Stata code is a little cryptic
  group_by(brgy_penetration) %>%
  mutate(sd_totbal = sd(totbal),
         mean_totbal = mean(totbal)) %>%
  ungroup()

combined <- combined %>%
  # create control dummy
  mutate(control = as.numeric(group == "C")) %>%
  # create distance to bank variable
  mutate(dist_GB = 
           case_when(
             butuan == 1 ~ dbutuan,
             ampayon == 1 ~ dampayon
           )
  )

# create a set with the 1777 observations that are in the SEED, 
# marketing treatment, or control group
treated <- combined %>%
  filter(!is.na(treatment))

@@

```{r}
#
# Create a plot to show the skew of balchange
#
skewa <- six_months %>%
  ggplot(aes(balchange)) +
  geom_density() +
  scale_x_continuous(labels = scales::comma) +
  scale_y_continuous(limits = c(0, 0.004)) +
  labs(title = "The Dependent Variables Are Highly Right Skewed",
       subtitle = "Six Month Change in Balance",
       x = "Change in balance (Philippine Peso)",       
       y = NULL) +
  theme_minimal()

skewb <- treated %>%
  ggplot(aes(balchange)) +
  geom_density() +
  scale_x_continuous(labels = scales::comma) +
  scale_y_continuous(limits = c(0, 0.004)) +
  labs(title = "",
       subtitle = "Twelve Month Change in Balance",
       x = "Change in balance (Philippine Peso)",
       y = NULL) +  
  theme_minimal()

@@

```{r}
#
# Create a plot to show the skew of balchange by group
#
skewa <- six_months %>%
  ggplot(aes(balchange, y = group, color = group)) +
  geom_point(alpha = 0.2) +
  scale_x_continuous(labels = scales::comma) +
  labs(title = "The Dependent Variables Are Highly Right Skewed",
       subtitle = "Six Month Change in Balance",
       x = "Change in balance (Philippine Peso)",       
       y = NULL) +
  theme_minimal() +
  guides(color = FALSE)

skewb <- treated %>%
  ggplot(aes(balchange, y = group, color = group)) +
  geom_point(alpha = 0.2) +
  scale_x_continuous(labels = scales::comma) +
  labs(title = "",
       subtitle = "Twelve Month Change in Balance",
       x = "Change in balance (Philippine Peso)",
       y = NULL) +  
  theme_minimal() +
  guides(color = FALSE)

@@

```{r}
#
# Count the types of change in balchange
# 
treated <-  treated %>%
  mutate(change =
           case_when(
             balchange > 0 ~ "Increase",
             balchange == 0 ~ "No Change",
             balchange < 0 ~ "Decrease"
           )
  ) %>%
  mutate(change = factor(change, levels = c("Decrease", "No Change", "Increase")))

@@

```{r results = "asis"}
#
# OLS model
#
six_months <- filter(seed011204, !is.na(treatment))

# column 1
lm1 <- lm(balchange ~ treatment + marketing, data = six_months) 
se1 <- lm1 %>% coeftest(vcov = vcovHC(., type="HC1"))

# column 2
lm2 <- lm(balchange ~ treatment, 
          data = filter(six_months, group %in% c("M", "T"))) 
se2 <- lm2 %>% coeftest(vcov = vcovHC(., type="HC1"))

# column 3
lm3 <- lm(balchange ~ treatment + marketing, data = treated) 
se3 <- lm3 %>% coeftest(vcov = vcovHC(., type="HC1"))

# column 4
lm4 <- lm(balchange ~ treatment, 
          data = filter(treated, group %in% c("M", "T"))) 
se4 <- lm4 %>% coeftest(vcov = vcovHC(., type="HC1"))

@@

# column 1
m_model1 <- rlm(balchange ~ treatment + marketing, method = "M", psi = psi.bisquare, data = six_months)

# column 2
m_model2 <- rlm(balchange ~ treatment, method = "M", psi = psi.bisquare, 
    data = filter(six_months, group %in% c("M", "T")))

# column 3
m_model3 <- rlm(balchange ~ treatment + marketing, method = "M", psi = psi.bisquare, data = treated)

# column 4
m_model4 <- rlm(balchange ~ treatment, method = "M", psi = psi.bisquare, 
    data = filter(treated, group %in% c("M", "T")))

@@

# column 1
rank_model1 <- rfit(balchange ~ treatment + marketing, data = six_months)

# column 2
rank_model2 <- rfit(balchange ~ treatment, 
     data = filter(six_months, group %in% c("M", "T")))

# column 3
rank_model3 <- rfit(balchange ~ treatment + marketing, data = treated)

# column 4
rank_model4 <- rfit(balchange ~ treatment, 
     data = filter(treated, group %in% c("M", "T")))

@@

lm3 <- lm(balchange ~ treatment + marketing, data = treated) %>%
  coeftest(vcov = vcovHC(., type="HC1"))

coefficients <- bind_rows(
  tibble(
    model = "OLS Model",
    tidy(lm3)
  ),
  tibble(
    model = "M Model",
    tidy(m_model3)
  ),
  tibble(
    model = "Rank-Based\nModel",
    term = c("(Intercept)", "treatment", "marketing"),
    estimate = rank_model3$coefficients,
    std.error = coef(summary(rank_model3))[, 2]
  )
)

@@

lm4 <- lm(balchange ~ treatment, 
   data = filter(treated, group %in% c("M", "T"))) %>%
  coeftest(vcov = vcovHC(., type="HC1"))

coefficients <- bind_rows(
  tibble(
    model = "OLS Model",
    tidy(lm4)
  ),
  tibble(
    model = "M Model",
    tidy(m_model4)
  ),
  tibble(
    model = "Rank-Based\nModel",
    term = c("(Intercept)", "treatment"),
    estimate = rank_model4$coefficients,
    std.error = coef(summary(rank_model4))[, 2]
  )
)

>>>>

```{r load-data}
seed011204 =read_stata("dataverse_files/seedanalysis_011204_1.dta")

seed080404 = read_stata("dataverse_files/seedanalysis_080404_1.dta")

combined = read_stata("dataverse_files/seedanalysis_011204_080404_1.dta")

six_months = filter(seed011204, !is.na(treatment))

@@

combined = combined  %>%
  # turn dollars into hundreds of dollars
  mutate(
    totbal = totbal / 100,
    newtotbal = newtotbal / 100
  ) %>%
  # fix population variable
  mutate(pop = as.numeric(str_replace(pop, ",", ""))) %>%
  # create bank penetration variable%>%
  mutate(brgy_penetration = no_clients / pop)

combined = combined %>%
  # calculate the mean and sd for each bank
  # the Stata code is a little cryptic
  group_by(brgy_penetration) %>%
  mutate(sd_totbal = sd(totbal),
         mean_totbal = mean(totbal)) %>%
  ungroup()

combined = combined %>%
  # create control dummy
  mutate(control = as.numeric(group == "C")) %>%
  # create distance to bank variable
  mutate(dist_GB = 
           case_when(
             butuan == 1 ~ dbutuan,
             ampayon == 1 ~ dampayon
           )
  )

# create a set with the 1777 observations that are in the SEED, 
# marketing treatment, or control group
treated = combined %>%
  filter(!is.na(treatment))

@@

```{r}
#
# Create a plot to show the skew of balchange
#
skewa = six_months %>%
  ggplot(aes(balchange)) +
  geom_density() +
  scale_x_continuous(labels = scales::comma) +
  scale_y_continuous(limits = c(0, 0.004)) +
  labs(title = "The Dependent Variables Are Highly Right Skewed",
       subtitle = "Six Month Change in Balance",
       x = "Change in balance (Philippine Peso)",       
       y = NULL) +
  theme_minimal()

skewb = treated %>%
  ggplot(aes(balchange)) +
  geom_density() +
  scale_x_continuous(labels = scales::comma) +
  scale_y_continuous(limits = c(0, 0.004)) +
  labs(title = "",
       subtitle = "Twelve Month Change in Balance",
       x = "Change in balance (Philippine Peso)",
       y = NULL) +  
  theme_minimal()

@@

```{r}
#
# Create a plot to show the skew of balchange by group
#
skewa = six_months %>%
  ggplot(aes(balchange, y = group, color = group)) +
  geom_point(alpha = 0.2) +
  scale_x_continuous(labels = scales::comma) +
  labs(title = "The Dependent Variables Are Highly Right Skewed",
       subtitle = "Six Month Change in Balance",
       x = "Change in balance (Philippine Peso)",       
       y = NULL) +
  theme_minimal() +
  guides(color = FALSE)

skewb = treated %>%
  ggplot(aes(balchange, y = group, color = group)) +
  geom_point(alpha = 0.2) +
  scale_x_continuous(labels = scales::comma) +
  labs(title = "",
       subtitle = "Twelve Month Change in Balance",
       x = "Change in balance (Philippine Peso)",
       y = NULL) +  
  theme_minimal() +
  guides(color = FALSE)

@@

```{r}
#
# Count the types of change in balchange
# 
treated =  treated %>%
  mutate(change =
           case_when(
             balchange > 0 ~ "Increase",
             balchange == 0 ~ "No Change",
             balchange < 0 ~ "Decrease"
           )
  ) %>%
  mutate(change = factor(change, levels = c("Decrease", "No Change", "Increase")))

@@

```{r results = "asis"}
#
# OLS model
#
six_months = filter(seed011204, !is.na(treatment))

# column 1
lm1 = lm(balchange ~ treatment + marketing, data = six_months) 
se1 = lm1 %>% coeftest(vcov = vcovHC(., type="HC1"))

# column 2
lm2 = lm(balchange ~ treatment, 
         data = filter(six_months, group %in% c("M", "T"))) 
se2 = lm2 %>% coeftest(vcov = vcovHC(., type="HC1"))

# column 3
lm3 = lm(balchange ~ treatment + marketing, data = treated) 
se3 = lm3 %>% coeftest(vcov = vcovHC(., type="HC1"))

# column 4
lm4 = lm(balchange ~ treatment, 
         data = filter(treated, group %in% c("M", "T"))) 
se4 = lm4 %>% coeftest(vcov = vcovHC(., type="HC1"))

@@

# column 1
m_model1 = rlm(balchange ~ treatment + marketing, method = "M", psi = psi.bisquare, data = six_months)

# column 2
m_model2 = rlm(balchange ~ treatment, method = "M", psi = psi.bisquare, 
               data = filter(six_months, group %in% c("M", "T")))

# column 3
m_model3 = rlm(balchange ~ treatment + marketing, method = "M", psi = psi.bisquare, data = treated)

# column 4
m_model4 = rlm(balchange ~ treatment, method = "M", psi = psi.bisquare, 
               data = filter(treated, group %in% c("M", "T")))

@@

# column 1
rank_model1 = rfit(balchange ~ treatment + marketing, data = six_months)

# column 2
rank_model2 = rfit(balchange ~ treatment, 
                   data = filter(six_months, group %in% c("M", "T")))

# column 3
rank_model3 = rfit(balchange ~ treatment + marketing, data = treated)

# column 4
rank_model4 = rfit(balchange ~ treatment, 
                   data = filter(treated, group %in% c("M", "T")))

@@

lm3 = lm(balchange ~ treatment + marketing, data = treated) %>%
  coeftest(vcov = vcovHC(., type="HC1"))

coefficients = bind_rows(
  tibble(
    model = "OLS Model",
    tidy(lm3)
  ),
  tibble(
    model = "M Model",
    tidy(m_model3)
  ),
  tibble(
    model = "Rank-Based\nModel",
    term = c("(Intercept)", "treatment", "marketing"),
    estimate = rank_model3$coefficients,
    std.error = coef(summary(rank_model3))[, 2]
  )
)

@@

lm4 = lm(balchange ~ treatment, 
         data = filter(treated, group %in% c("M", "T"))) %>%
  coeftest(vcov = vcovHC(., type="HC1"))

coefficients = bind_rows(
  tibble(
    model = "OLS Model",
    tidy(lm4)
  ),
  tibble(
    model = "M Model",
    tidy(m_model4)
  ),
  tibble(
    model = "Rank-Based\nModel",
    term = c("(Intercept)", "treatment"),
    estimate = rank_model4$coefficients,
    std.error = coef(summary(rank_model4))[, 2]
  )
)
